### 2016-08-04 architecture.tex
Warn about using wildcard imports
This part was removed from mpmath section and added
to the introduction, as footnote.

This address point 2 of the reviewer 2.

The following statement
imports all SymPy functions into the global Python namespace.
From here on, all examples in this paper assume that this statement has been
executed.\footnote{All examples in this paper use SymPy version 1.0.}

>>>>

The following statement
imports all SymPy functions into the global Python namespace.\footnote{
Nevertheless, it is best to avoid such wildcard import statements
in production code, as they make it unclear which names are present
in the namespace and injected names could clash with already existing
imports from another package.  For example, both SymPy and standard
Python \texttt{math} library define the \texttt{exp} function.}
From here on, all examples in this paper assume that this statement has been
executed.\footnote{All examples in this paper use SymPy version 1.0.}
